Practical Machine Learning Class Project
========================================================

We can start with loading the data and useful packages.
```{r include=FALSE}
setwd("/Users/xiaoxuwu/Documents/coursera/PML")
```

```{r message=FALSE}
training <- read.csv("pml-training.csv")
testing <- read.csv("pml-testing.csv")
library(caret)
library(randomForest)
```

9DoF sensor data including magnetometers, gyroscopes, accelerometers and yaw-pitch-roll orientation for the four sensors are used in the model.

```{r}
mod <- randomForest(classe~roll_belt+pitch_belt+pitch_belt+gyros_belt_x+gyros_belt_y+gyros_belt_z+accel_belt_x+accel_belt_y+accel_belt_z+magnet_belt_x+magnet_belt_y+magnet_belt_z+roll_arm+pitch_arm+pitch_arm+gyros_arm_x+gyros_arm_y+gyros_arm_z+accel_arm_x+accel_arm_y+accel_arm_z+magnet_arm_x+magnet_arm_y+magnet_arm_z+roll_dumbbell+pitch_dumbbell+pitch_dumbbell+gyros_dumbbell_x+gyros_dumbbell_y+gyros_dumbbell_z+accel_dumbbell_x+accel_dumbbell_y+accel_dumbbell_z+magnet_dumbbell_x+magnet_dumbbell_y+magnet_dumbbell_z+roll_forearm+pitch_forearm+pitch_forearm+gyros_forearm_x+gyros_forearm_y+gyros_forearm_z+accel_forearm_x+accel_forearm_y+accel_forearm_z+magnet_forearm_x+magnet_forearm_y+magnet_forearm_z,data=training)
```

The confusion matrix shows that this model is a good fit for the training dataset.
```{r}
mod$confusion
```
Now, we evaluate the model with cross-validation.
```{r}
set.seed(12345)
error <- c()
for(i in 1:10){
    intrain = sample(1:dim(training)[1],size=dim(training)[1]/10*9,replace=F)
    trainCross = training[intrain,]
    testCross = training[-intrain,]
    modCross <- randomForest(classe~roll_belt+pitch_belt+pitch_belt+gyros_belt_x+gyros_belt_y+gyros_belt_z+accel_belt_x+accel_belt_y+accel_belt_z+magnet_belt_x+magnet_belt_y+magnet_belt_z+roll_arm+pitch_arm+pitch_arm+gyros_arm_x+gyros_arm_y+gyros_arm_z+accel_arm_x+accel_arm_y+accel_arm_z+magnet_arm_x+magnet_arm_y+magnet_arm_z+roll_dumbbell+pitch_dumbbell+pitch_dumbbell+gyros_dumbbell_x+gyros_dumbbell_y+gyros_dumbbell_z+accel_dumbbell_x+accel_dumbbell_y+accel_dumbbell_z+magnet_dumbbell_x+magnet_dumbbell_y+magnet_dumbbell_z+roll_forearm+pitch_forearm+pitch_forearm+gyros_forearm_x+gyros_forearm_y+gyros_forearm_z+accel_forearm_x+accel_forearm_y+accel_forearm_z+magnet_forearm_x+magnet_forearm_y+magnet_forearm_z,data=trainCross)
    prediction <- predict(modCross, testCross)
    e <- sum(prediction != testCross$classe)/length(prediction)
    error <- c(error,e)
}
```

The cross-validation error rate is shown below.
```{r}
error
mean(error)
```

Now that the proposed model is satisfactory. We can apply it to the testing set and generate the result as below
```{r}
predict(mod, testing)
pml_write_files = function(x){
  n = length(x)
  for(i in 1:n){
    filename = paste0("problem_id_",i,".txt")
    write.table(x[i],file=filename,quote=FALSE,row.names=FALSE,col.names=FALSE)
  }
}
pml_write_files(predict(mod,testing))
```
